\documentclass[11pt]{report}

\usepackage{listings}
\usepackage[left=1in, right=1in, top=1in]{geometry}
\usepackage{amsmath}
\usepackage{url}

\title{\textbf{Using Linear Algebra Libraries in C++ and Python}}
\author{Melvyn Ian Drag}
\date{\today}

\begin{document}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
In this paper I will describe what BLAS, LAPACK, and ATLAS are. Then I will show how to write C++ code which uses these libraries to perform common linear algebra operations like matrix-matrix, and matrix-vector multiplication, and LU factorization. I will then compare the FLOPS of the multiplication codes to some highly optimized tiled and row-permuted multiplication code I have written to (hopefully) show the the incredible speed ups possible with these libraries. 

Many people on stackoverflow.com are clamoring for a paper such as this one. I plan on posting a link to this paper in response to several questions I have seen online.

I will also show how these libraries are utilized in a correctly built scipy/numpy  package, demonstrating that scientific python codes can indeed run fast.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Dedication
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \clearpage
 \newgeometry{textwidth=10cm}
 \emph{I looked around and could only find these two webpages with some simple examples. I wish more people would add examples of codes to use these libraries. }- makhlaghi, Stackoverflow.com user.\\
\begin{center}
This paper is for you, for all of those like you (including myself) who have been confused about how to use these popular but suprisingly poorly documented libraries!
\end{center}
\restoregeometry
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CONTENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \tableofcontents{}
\input{./intro.tex}
\input{./mm.tex}
\input{./lu.tex}
\end{document}
